Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-22 MS_thesis.tex
Minor rephrasing of acknowledgements

Finally, I am eternally indebted to my parents, Raja and Vidya. They have unfailingly supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest with no cellular network catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of fully committing to the pipe dream of getting admission in an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo. Thank you for always believing in me and letting me make my own choices; I would be nothing without you. 
}
\allowdisplaybreaks %allow align envts to go across pages

>>>>

Finally, I am eternally indebted to my parents, Raja and Vidya. They have unfailingly supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest with no cellular network catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of fully committing to the pipe dream of getting accepted by an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo. Thank you for always believing in me and letting me make my own choices, both small and large; I would be nothing without you. 
}
\allowdisplaybreaks %allow align envts to go across pages
